Psychological Needs During Intergroup Contact

### 2021-12-16 manuscript.tex

% Problem v.02: theoretical interaction quality central to understanding outcomes, practical many impactful negative interactions in everyday life
There are however substantial theoretical and practical consequences of these understudied mechanisms of everyday intergroup contact. Theoretically, interaction quality or -valence sits at the heart of intergroup contact theory, as it gauges whether the interaction will result to positive intergroup outcomes \citep[][]{Tropp2016, Brown2007}. And practically, a longstanding body of literature, has been showing that negative interactions are common in everyday life and often result in a substantial decline of intergroup relations \citep[][]{Barlow2012, Shelton2009}. It is thus important that we explore which psychological mechanisms explain when and why intergroup contacts are positive and lead to better intergroup perceptions, especially during everyday intergroup encounters \citep[e.g.,][]{MacInnis2015}.

>>>>

% Problem v.02: theoretical interaction quality central to understanding outcomes, practical many impactful negative interactions in everyday life
There are however substantial theoretical and practical consequences of these understudied mechanisms of everyday intergroup contact. Theoretically, interaction quality or -valence sits at the heart of intergroup contact theory, as it gauges whether the interaction will result in positive intergroup outcomes \citep[][]{Tropp2016, Brown2007}. Practically, a longstanding body of literature has shown that negative interactions are common in everyday life and often result in a substantial decline of intergroup relations \citep[][]{Barlow2012, Shelton2009}. It is thus important to explore which psychological mechanisms explain when and why intergroup contacts are positive and lead to better intergroup perceptions, especially during everyday intergroup encounters \citep[e.g.,][]{MacInnis2015}.
